Red-Giant Hot Jupiters: Brilliant Radio Emitter?

### 2015-05-18 ms.tex
Added spiegel+burrows2012

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}. 
For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
%%%%%%%%%% 
\begin{equation}
\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}. The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core. 
In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$. 
%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bp]
 %\begin{minipage}{0.5\hsize}
  %\begin{center}
   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
   \plotonesc{radio_emission_Mdot1e-8_constRp.pdf}
  %\end{center}
 %\end{minipage}
 %\begin{minipage}{0.5\hsize}
   %\begin{center}
   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
   \plotonesc{radio_emission_Mdot1e-5_constRp.pdf}
  %\end{center} 
 %\end{minipage}
   \caption{[{\bf Old version: based on scaling relationship of Sano 1993}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc. The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere. The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion. Bottom panel: cyclotron frequency, i.e., the frequency of radio emission. }
  \label{fig:radio}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007, spiegel+burrows2012}.
For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
%%%%%%%%%% 
\begin{equation}
\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}. The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core. 
In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$. 
%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bp]
 %\begin{minipage}{0.5\hsize}
  %\begin{center}
   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
   \plotonesc{radio_emission_Mdot1e-8_constRp.eps}
  %\end{center}
 %\end{minipage}
 %\begin{minipage}{0.5\hsize}
   %\begin{center}
   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
   \plotonesc{radio_emission_Mdot1e-5_constRp.eps}
  %\end{center} 
 %\end{minipage}
   \caption{[{\bf Old version: based on scaling relationship of Sano 1993}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc. The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere. The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion. Bottom panel: cyclotron frequency, i.e., the frequency of radio emission. }
  \label{fig:radio}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
